Figures

### 2019-07-16 figures/08_exploratory_dotplot.Rmd
rename variable categories

prep_dotplot <- function(x, col_name){
  # x <- dt_tp
  # col_name <- "tp"
  pred_key <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)
  res      <- x %>%
    dplyr::select(UQ(rlang::sym(col_name))) %>%
    # dplyr::filter(!is.na(UQ(rlang::sym(col_name)))) %>%
    dplyr::mutate(var = row.names(x)) %>%
    dplyr::left_join(pred_key, by = "var") %>%
    dplyr::mutate(var = factor(row.names(x), 
                            levels = rev(row.names(x))), 
                  pretty = factor(pretty, levels = rev(pretty)),
                  category = factor(category, 
                                    levels = c("Lake", "Nutrient sources",
                                               "Nutrient proxies",
                                               "Transport capacity", 
                                               "Buffer composition"))) %>%
    dplyr::filter(!(var %in% c("tp", "tn"))) %>%
    dplyr::filter(!is.na(category))
  res
}

>>>>

prep_dotplot <- function(x, col_name){
  # x <- dt_tp
  # col_name <- "tp"
  pred_key <- read.csv("../data/predictor_key.csv", stringsAsFactors = FALSE)
  res      <- x %>%
    dplyr::select(UQ(rlang::sym(col_name))) %>%
    # dplyr::filter(!is.na(UQ(rlang::sym(col_name)))) %>%
    dplyr::mutate(var = row.names(x)) %>%
    dplyr::left_join(pred_key, by = "var") %>%
    dplyr::mutate(var = factor(row.names(x), 
                            levels = rev(row.names(x))), 
                  pretty = factor(pretty, levels = rev(pretty)),
                  category = factor(category, 
                                    levels = c("Nutrient inputs",
                                               "Nutrient transport", 
                                               "Land-use cover",
                                               "Buffer composition", 
                                               "Lake"))) %>%
    dplyr::filter(!(var %in% c("tp", "tn"))) %>%
    dplyr::filter(!is.na(category))
  res
}
